Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2015-02-14 papers/wdmerger_I/paper.tex
Add reference to the location of this software.

We track a number of diagnostic quantities at the end of every coarse grid timestep. 
For all simulations, we record the total energy (including the breakdown into
its components: kinetic, internal, gravitational potential, rotation), 
the total angular momentum, and the center of mass of the system. 
For stellar calculations, we separately record diagnostic 
information about the stars, including their centers of mass, 
and the volume contained within each star.

>>>>

We track a number of diagnostic quantities at the end of every coarse grid timestep. 
For all simulations, we record the total energy (including the breakdown into
its components: kinetic, internal, gravitational potential, rotation; we note
that for the diagnostics we actually use $(\rho E)$ for calculation of the total energy,
rather than explicitly calculating the sum of kinetic and internal, as this is
the quantity that should be explicitly conserved), 
the total angular momentum, and the center of mass of the system. 
For stellar calculations, we separately record diagnostic 
information about the stars, including their centers of mass, 
and the volume contained within each star.

The software used to generate the test problems in this paper
(as well as the paper text itself),
\texttt{wdmerger}\footnote{\url{https://github.com/BoxLib-Codes/wdmerger}},
is freely available at an online repository hosting service.
Version control in both the parent software (BoxLib, CASTRO) and in \texttt{wdmerger}
permits us to reference the state of the code at the time a simulation
was performed. To do so, in all plot files generated we store
the complete set of parameters used in that simulation. We also store the 
version commit hashes of the parent software in the plot files.
We store the commit hashes of all three as comments in the metadata of 
any EPS files generated as figures in this paper.
